% 'nonacm' to remove any running header
\documentclass[nonacm,sigconf]{acmart}

\usepackage{cite}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{tagging}

\usepackage{sc25repro}
\pagenumbering{gobble} % no page numbers

\begin{document}

\twocolumn[%
{\begin{center}
\Huge
Appendix: Artifact Description
\end{center}}
]

\appendixAD

\section{Overview of Contributions and Artifacts}

\subsection{Paper's Main Contributions}

\begin{description}
\item[$C_1$] We introduce a prototype-based approximate lookup table (ALUT)
mechanism for accelerating MoE-based MLLMs by replacing redundant expert
execution with approximate lookup and reuse.
\item[$C_2$] We design a sliding-window reuse cache that exploits in-context
locality during decoding to improve approximation fidelity and preserve model
accuracy.
\item[$C_3$] We propose an expert-level importance-aware scheduler that
selects which experts should be recomputed exactly and which can be served via
approximate reuse.
\item[$C_4$] We present an experimental evaluation showing that TableMoE
reduces TTFT and TPOT while maintaining high task accuracy without retraining.
\end{description}

\subsection{Computational Artifacts}

\begin{description}
\item[$A_1$] Artifact archive DOI: N/A at the AD stage. The current public
artifact consists of the TableMoE source repository
(\url{https://github.com/fanyalun/tablemoe-sc26.git}) and the released offline
tables for the default Qwen path (Hugging Face bucket
\texttt{fanyafanya/ALUTs}). This appendix focuses on the default
single-GPU/single-NUMA reproduction path for
\texttt{Qwen3-VL-30B-A3B-Instruct}.
\end{description}

\begin{center}
\begin{tabular}{rll}
\toprule
Artifact ID  &  Contributions &  Related \\
             &  Supported     &  Paper Elements \\
\midrule
$A_1$   &  $C_1$ & Table III, Figure 11, Figure 12 \\
\midrule
$A_1$   &  $C_2$ & Figure 11, Figure 12 \\
\midrule
$A_1$   &  $C_3$ & Figure 12, Figure 14, Figure 15 \\
\midrule
$A_1$   &  $C_4$ & Table II, Figures 9--15 \\
\bottomrule
\end{tabular}
\end{center}

\section{Artifact Identification}

\newartifact

\artrel

This artifact contains the implementation of TableMoE, including the offline
ALUT construction pipeline, the runtime reuse/cache/scheduling logic, and the
evaluation scripts used to measure latency and accuracy. The same artifact is
used to support all four contributions of the paper. The minimum reproduction
path in this appendix uses the default Qwen single-GPU configuration, while the
repository keeps the parameterized evaluation entrypoints that are used for the
broader paper results.

\artexp

The minimum reproduction path is expected to generate three summary outputs:
(1) a TTFT/TPOT summary from \texttt{eval\_perf}, (2) a lightweight accuracy
comparison written by \texttt{eval\_perf}, and (3) an accuracy summary written
by \texttt{eval\_acc}. Under the default settings, TableMoE should show lower
prefilling latency than the default offloading baselines in the quick
reproduction path (\texttt{adapmoe} and \texttt{skip}), while preserving model
quality close to the \texttt{transformers} baseline in the accuracy evaluation.
The same repository also contains the parameterized scripts used to regenerate
the wider paper result set, including Table II, Table III, and Figures 9--15.

\arttime

\begin{description}
\item[Setup] 10--30 minutes. This covers cloning the repository, creating the
Python environment, and installing the dependencies for the minimum path.
\item[Optional offline-table preparation] Downloading the released offline
tables takes 10--20 minutes. Rebuilding the offline tables locally takes about
2--3 hours, depending on storage speed and the time required to profile and
cluster routed hidden states.
\item[Execution] Running \texttt{eval\_perf} takes about 20--30 minutes for the
default RealWorldQA path. Running \texttt{eval\_acc} takes about 2 hours for
the same default path.
\item[Analysis] Less than 5 minutes. The scripts write the main comparison
tables directly to the result directories.
\end{description}

\artin

\artinpart{Hardware}

All experiments in the minimum reproduction path are conducted on a CPU--GPU
heterogeneous platform using one NUMA node of an Intel Xeon Gold 5318Y CPU
(24 cores), 256~GB DDR4 memory, and one NVIDIA A100 PCIe GPU with 80~GB HBM,
connected via PCIe~4.0~$\times$16.

\artinpart{Software}

The validated software stack for the minimum reproduction path is:
\begin{itemize}
\item Ubuntu 22.04.4 LTS (\url{https://ubuntu.com/})
\item Python 3.10.18 (\url{https://www.python.org/})
\item CUDA 12.8 (\url{https://developer.nvidia.com/cuda-toolkit})
\item NVIDIA Driver 580.95.05 (\url{https://www.nvidia.com/drivers})
\item PyTorch 2.8.0+cu128 (\url{https://pytorch.org/})
\item torchvision 0.23.0+cu128
(\url{https://pytorch.org/vision/stable/index.html})
\item transformers 4.57.0
(\url{https://github.com/huggingface/transformers})
\item flash-attn 2.7.3
(\url{https://github.com/Dao-AILab/flash-attention})
\item triton 3.4.0 (\url{https://github.com/triton-lang/triton})
\item TableMoE repository
(\url{https://github.com/fanyalun/tablemoe-sc26.git})
\end{itemize}
The minimum path does not require CUTLASS, MoE-Infinity, Pregated-MoE, or a
local judge model.

\artinpart{Datasets / Inputs}

The minimum reproduction path requires the following inputs:
\begin{itemize}
\item Model checkpoint: \texttt{Qwen/Qwen3-VL-30B-A3B-Instruct}, downloaded by
\texttt{bash scripts/download\_model.sh}.
\item Benchmark TSV file: \texttt{RealWorldQA.tsv}, downloaded by
\texttt{bash LMUData/download\_datasets.sh}.
\item Optional released offline table for the default Qwen path, downloaded by
\texttt{bash offline\_table/download\_offline\_table.sh}.
\end{itemize}

The repository also supports the paper's other public benchmarks
(\texttt{MMBench\_DEV\_EN\_V11}, \texttt{AI2D\_TEST},
\texttt{ScienceQA\_TEST}, and \texttt{POPE}) through the same download and
evaluation entrypoints. For the Qwen model, released offline tables are
currently published for \texttt{RealWorldQA}, \texttt{MMBench\_DEV\_EN\_V11},
and \texttt{AI2D\_TEST}. The default evaluation scripts can automatically fetch
missing published Qwen offline tables when \texttt{HF\_AUTO\_DOWNLOAD=1}
(default). Any remaining offline tables can be generated locally with
\texttt{bash offline\_table/run\_offline\_table.sh}.

\artinpart{Installation and Deployment}

The minimum path only needs a standard Python environment:

{\small
\begin{verbatim}
git clone https://github.com/fanyalun/tablemoe-sc26.git
cd tablemoe-sc26
conda create -n tablemoe python=3.10.18 -y
conda activate tablemoe
pip install torch==2.8.0 torchvision==0.23.0
pip install -r requirements.txt
pip install flash-attn==2.7.3 --no-build-isolation
\end{verbatim}
}

If a prebuilt flash-attn wheel is unavailable for the local environment, the
same CUDA 12.8 toolchain must be used to build it locally. No additional
third-party baseline compilation is required for the minimum path described in
this appendix.

\artcomp

The minimum-path workflow is:
\begin{description}
\item[$T_1$] Prepare the environment and install the dependencies.
\item[$T_2$] Download the default Qwen checkpoint and the RealWorldQA TSV file.
\item[$T_3$] Optionally prepare the offline table. This can be done explicitly
by downloading the released table or by rebuilding it locally. When the
published Qwen table is missing, the default evaluation scripts can also
download it automatically through the built-in \texttt{HF\_AUTO\_DOWNLOAD=1}
path.
\item[$T_4$] Run the default performance benchmark with
\texttt{adapmoe}, \texttt{skip}, and \texttt{tablemoe}.
\item[$T_5$] Run the default accuracy benchmark with
\texttt{transformers}, \texttt{skip}, and \texttt{tablemoe}.
\end{description}

The workflow dependency is
$T_1 \rightarrow T_2 \rightarrow T_3 \rightarrow T_4 \rightarrow T_5$, where
$T_3$ is optional when automatic offline-table download succeeds.

The public parameters exposed by the repository include \texttt{MODEL}
(default \texttt{Qwen3-VL-30B-A3B-Instruct}), \texttt{DATASETS}
(default \texttt{RealWorldQA}), \texttt{METHODS}, \texttt{CACHE\_RATIO},
\texttt{KEEP\_RATE}, and \texttt{SAMPLE\_RATIO}. The minimum path uses
\texttt{CACHE\_RATIO=0.5}, \texttt{KEEP\_RATE=0.6}, and
\texttt{SAMPLE\_RATIO=0.1} for \texttt{eval\_perf}. For
\texttt{eval\_acc}, we use \texttt{CACHE\_RATIO=1.0} so that all routed
experts stay resident on GPU and the accuracy comparison is not dominated by
offloading variance. The default \texttt{MAX\_NEW\_TOKENS} is 2048.

The minimum reproduction commands are:

{\small
\begin{verbatim}
bash scripts/download_model.sh
bash LMUData/download_datasets.sh

# Optional: prepare the released offline table explicitly.
bash offline_table/download_offline_table.sh

CUDA_VISIBLE_DEVICES=0 METHODS="adapmoe,skip,tablemoe" \
bash eval_perf/eval_perf.sh

CUDA_VISIBLE_DEVICES=0 METHODS="transformers,skip,tablemoe" \
CACHE_RATIO=1.0 bash eval_acc/eval_acc.sh
\end{verbatim}
}

\artout

The main outputs are written directly to disk:
\begin{itemize}
\item \path{perf_results/default/summary/perf_table.json}
\item \path{perf_results/default/summary/perf_table.csv}
\item \path{perf_results/default/summary/perf_table.md}
\item \path{perf_results/default/summary/simple_accuracy_table.json}
\item \path{perf_results/default/summary/simple_accuracy_table.csv}
\item \path{perf_results/default/summary/simple_accuracy_table.md}
\item \path{acc_results/default/summary/accuracy_table.json}
\item \path{acc_results/default/summary/accuracy_table.csv}
\item \path{acc_results/default/summary/accuracy_table.md}
\end{itemize}

The latency comparison is taken from \texttt{eval\_perf}, while the accuracy
comparison in this appendix is taken from \texttt{eval\_acc}. These result
files are the primary outputs used to compare TableMoE with the default
baselines in the minimum path. The same evaluation entrypoints, when run with
other public datasets and parameter settings, support the broader paper result
set summarized in Table II, Table III, and Figures 9--15.

\end{document}
